\LARGE \bf Cross Validation of Emotional Features with a non-Anthropomorphic Platform

### 2017-06-10 RO-MAN-2017-1/Parts/Results.tex
Reviewed

An analysis was done per groups, for each presented emotion. For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This leads to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

@@

\begin{itemize}
	\item $H_0 = $ there is a difference in recognition between the implementation with respect to the others.
	\item $H_1 = $ there is not a difference in recognition between one implementation with respect to the others.
\end{itemize}

The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compared with other implementations. While both implementations of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.

@@

Nevertheless, it is important to notice that the results were obtained using the lower part of the robot without any change in its shape. Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate. As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level. In this precise case, the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

>>>>

An analysis was done per groups, for each presented emotion. For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when  another one was presented, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This leads to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

@@

\begin{itemize}
	\item $H_0 = $ there is a difference in recognition between the implementation with respect to the others.
	\item $H_1 = $ there is not a difference in recognition between the implementation with respect to the others.
\end{itemize}

The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that Anger-2, and both \textit{Fear} and \textit{Sadness} are considered as different from other implementations, while both implementations of \textit{Happiness} and Anger-1 are considered as similar to other implementations.

@@

It is important to notice that the results were obtained using the lower part of the robot without any change in its shape. Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate. As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level. In particular, \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the highest recognition rates (54\% for the first and 50\% for the second).
